WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-17 paper/ms.tex
update paper; ready for collaborators

\begin{abstract}
    The Transiting Exoplanet Survey Satellite (TESS) recently observed
    18 transits of the hot Jupiter WASP-4b.  The sequence of transits
    occurred $81.5 \pm 11.7$~seconds earlier than had been predicted,
    based on earlier data stretching back to 2007.  This is unlikely
    to be the result of a clock error, because TESS observations of
    other hot Jupiters (WASP-6b, 18b, and 46b) are compatible with a
    constant period, ruling out an 81.5-second offset at the
    6.4$\sigma$ level.  The 1.3-day orbital period of WASP-4b appears
    to be decreasing at a rate of $\dot{P} = -12.6 \pm 1.2$
    milliseconds per year.  This might be caused by tidal orbital
    decay or apsidal precession, although both interpretations have
    shortcomings.  The gravitational influence of a third body is another
    possibility, although at present there is scant evidence for such a
    body. Further observations are needed to confirm and
    understand the timing variation.
\end{abstract}

@@

Second, long-term timing studies may reveal apsidal precession, {\it
  i.e.}, the rotation of the orbital ellipse within the orbital
plane. Apsidal precession has long been observed in eclipsing binaries
\citep[{\it e.g.},][]{
  schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015}.
For exoplanets, precessing orbits have been detected in a handful of
cases, including circumbinary systems (Kepler-413
\citealt{kostov_kepler-413b_2014}; Kepler-453
\citealt{welsh_kepler_2015}, planets orbiting rapidly rotating stars
(Kepler-13
\citealt{szabo_spin-orbit_2012,szabo_mapping_2014},~\citealt{masuda_spin-orbit_2015};
and systems with multiple interacting giant planets (Kepler-108
\citealt{mills_kepler-108_2017}; Kepler-693
\citealt{masuda_eccentric_2017}).  Apsidal precession is not regularly
observed in hot Jupiter systems because their orbits are nearly
circular, which may itself be a consequence of star-planet tides.  If
it could be observed, then \citep{ragozzine_probing_2009} showed that
it would be possible to measure the planet's Love number, which would
be a valuable constraint on the planet's interior.

@@

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=0.49\textwidth]{f2.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Phase-folded lightcurve of WASP-4b.} Black points are
        TESS data. Yellow points are binned measurements.  The bottom
        panel shows the residuals.  The fit to the phase-folded
        transit (blue line) is used when measuring mid-transit times for
        the individual transits (Figure~\ref{fig:lightcurves}).
        \label{fig:phasefold}
    }
\end{figure}

@@

We began our analysis with the Presearch Data Conditioning (PDC)
lightcurve \citep{smith_kepler_apertures_2017,smith_kepler_PDC_2017}.
We processed the lightcurve as follows.  First, we removed all points
with non-zero quality flags.  This removed data contaminated by coarse
spacecraft pointing, cosmic rays, and other annoyances
\citep{tess_data_product_description_2018}.  We also removed the data
within the first and last hours of both orbits, because of ramp-like
systematic effects that appear during those time ranges. We also
removed the data that might have been adversely affected by ``momentum
dumps,'' the firing of thrusters and resetting of reaction wheels that
took place every 2.5 days during sector
2.\footnote{\url{archive.stsci.edu/hlsps/tess-data-alerts/hlsp_tess-data-alerts_tess_phot_s01_tess_v1_release-notes.pdf}}.
The data during these events were assigned quality flags corresponding
to ``Reaction Wheel Desaturation Event'' and ``Manual Exclude''.  For
WASP-4, these flags were simultaneously set for 54 distinct cadences,
and there were 10 momentum dumps, averaging about 10 minutes of
flagged data per dump.  Out of caution, we clipped out an additional
10 minutes before and after every momentum dump.

@@

Using the cleaned PDC lightcurve, we used the Box Least Squares
algorithm \citep{kovacs_box-fitting_2002} to estimate the orbital
period, transit duration, and a reference epoch using the TESS data
alone.  Based on the results, we isolated the data within 4 transit
durations of each transit midpoint.  We then fitted all of the transit
data using the analytic formulae given by \citet{mandel_analytic_2002}
and implemented by \citet{kreidberg_batman_2015}.  We assumed the
orbit to be circular. The free parameters were the reference epoch,
the planet to star radius ratio $R_{\rm p}/R_\star$, the orbital
distance to stellar radius ratio $a/R_\star$, the inclination $i$, two
quadratic limb-darkening coefficients $(u_{\rm linear}, u_{\rm
  quad})$, and the orbital period $P$.

@@

To measure the transit times, we fitted each transit separately, with
four free parameters: the time of mid-transit $t_{\rm tra}$, the
planet-to-star radius ratio, and the slope and intercept of a linear
trend to account for any slow variations unrelated to the transit.  We
fixed the remaining parameters at the values that had been determined
from the phase-folded TESS lightcurve.  The uncertainty in each
data point was set equal to the root-mean-square (rms) level of the
out-of-transit data.

To verify that the measured uncertainties are plausible, we computed
the reduced $\chi^2$ for a linear ephemeris fit to the measured TESS
transit times.  We found that $\chi^2 = 9.2$, with $n=16$ degrees of
freedom.  The variance of the $\chi^2$ distribution is $2n$, so we
would expect $\chi^2 16 \pm 5.7$.  Visually inspecting the residuals
showed that the error variance had been overestimated, so we
multiplied the measured TESS errors by a factor $f=0.76$, forcing a
reduced $\chi^2$ of unity.  This lowered the mean uncertainty of the
transit midtimes from $29.8$ to $22.6$ seconds.  We verified that
omitting this step did not appreciably alter any of our conclusions.

@@

\startdata
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.15117$              & $+0.00047$, $-0.00037$      & A \\
  $i$~[deg]                                  & $88.85$                & $+0.77$, $-0.90$            & A \\
  $a/R_\star$                                & $5.457$                & $+0.030$, $-0.066$          & A \\
  $u_{\rm linear}$                           & $0.388$                & ---                         & A \\
  $u_{\rm quad}$                             & $0.212$                & ---                         & A \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & B \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & C \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & C \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & C \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & D \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & F \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & E \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.717$                & $+0.029$, $-0.062$          & E \\
  $M_\star$~[M$_{\odot}$]                    & $0.867$                & $+0.087$, $-0.097$          & E \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & G \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0227$               & $\pm 0.0008$                & E \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.189$                & $+0.093$, $-0.104$          & E \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.314$                & $\pm 0.039$                 & E \\
\enddata

@@

We calculated the stellar and planetary parameters in the following
way.  We computed the star's spectral energy distribution based on the
{\it Gaia} DR2 parallax (after making the small correction advocated
by \citealt{stassun_evidence_2018}) and the broadband magnitudes from
all the available all-sky catalogs: $G$ from {\it Gaia\/} DR2, $B_T$
and $V_T$ from {\it Tycho-2}, $BVgri$ from {\it APASS}, $JHK_S$ from
{\it 2MASS}, and the {\it WISE}~1--4 passbands, thus spanning the
wavelength range 0.4--22~$\mu$m.  We adopted the effective temperature
from the work by \citet{doyle_accurate_2013}, who determined the
spectroscopic parameters of WASP-4 using high-signal-to-noise
observations with the High Accuracy Radial-velocity Planet Searcher
(HARPS).  Then, we determined the stellar radius through the
combination of the bolometric luminosity and the effective
temperature, using the Stefan-Boltzmann law.  To determine the stellar
mass, we first computed the mean stellar density based on the value of
$a/R_\star$ that gave the best fit to the phase-folded TESS lightcurve
(for the relevant equation, see \citealt{seager_unique_2003} or
\citealt{winn_exoplanet_2010}).  The mass was calculated from the
radius and density, and the orbital distance was also calculated from
the radius and $a/R_\star$.  The planetary radius was calculated as
the product of $R_\star$ and $R_{\rm p}/R_\star$.  Finally, the planet
mass was calculated based on the stellar mass, the radial-velocity
amplitude observed by \citet{triaud_spin-orbit_2010}, and the orbital
inclination.

@@

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{ {\bf TESS saw WASP-4b transit earlier than expected.}
      Both plots show the deviations between the observed and
      calculated transit times, where the calculation is based only on
      the pre-TESS data and assumes a constant period.  The blue bands
      depict the $\pm$$1\sigma$ credible interval of the predicted
      times.  {\it Top:} The full timing dataset spans 10 years. The
      darkest points correspond to the most precise data.  {\it
        Bottom:} Close-up of the TESS observations. The red band shows
      the average deviation of the TESS data, which is $81.5 \pm
      11.7\ {\rm seconds}$.
        \label{fig:arrived_early}
    }
\end{figure}

@@

We also compiled all the available occultation times, which are given
in Table~3.  The tabulated values have been corrected for the
light-travel time across the diameter of the orbit by subtracting
$2a/c = 22.8$ seconds from the observed time.
\citet{beerer_secondary_2011} observed two occultations of WASP-4b
using warm Spitzer in the 3.6\,$\mu$m and 4.5\,$\mu$m bands.
\citet{caceres_ground-based_2011} detected an occultation from the
ground in the $K_S$ band, and gave a time in HJD, without specifying
the time standard.  We assumed the standard was UTC, and performed the
appropriate corrections to convert to BJD$_{\rm TDB}$.  We
also verified that none of our conclusions would be changed if this
assumption was mistaken. Finally, \citet{zhou_secondary_2015} observed an
occultation with the the Anglo-Australian Telescope.  They did not
report the observed midpoint, but they did report a result for
$e\cos\omega$ based upon the observed midpoint.  We calculated the
implied midpoint using the formula \citep[{\it
e.g.},][]{winn_exoplanet_2010}
\begin{equation}
  t_{\rm occ}(E) =
  t_0 +  P E  +
  \frac{P}{2} \left( 1 + \frac{4}{\pi} e\cos\omega \right).
  \label{eq:occultation_time}
\end{equation}
In total, there are four occultation times.

@@

In the decreasing-period model, the period derivative is
\begin{equation}
\dot{P}
  = - (3.98 \pm 0.38)\times 10^{-10}
  = - (12.6 \pm 1.2)~{\rm ms}\,{\rm yr}^{-1}.
  \label{eq:dP_dt_obs}
\end{equation}
For comparison, the best-fitting period derivative of WASP-12b is
$\dot{P} = -29 \pm 3\,{\rm ms}\,{\rm yr}^{-1}$
\citep{maciejewski_departure_2016,patra_2017}.  If both planets are
truly falling onto their stars, then WASP-4b is falling at about half
the rate of WASP-12b.  In the precession model, the best-fit
eccentricity is
\begin{equation}
  e = (1.83^{+ 1.88}_{- 0.75})\times10^{-3}
\end{equation}
The longitude of periastron advances by $\dot{\omega} =
14.0^{+4.9}_{-3.5}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period is $26^{+9}_{-7}$ years.  All of the best-fitting parameters
(the medians of the posterior distributions) and the 68\% credible
intervals are reported in Table~4.

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.38\textwidth]{f5.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf WASP-4b in the context of other hot Jupiters.}
    Most of the data in these plots are from \citet{bonomo_gaps_2017},
    who measured the eccentricities using radial velocities.  The
    colored symbols highlight WASP-4, WASP-12 (which also shows
    evidence for a decreasing period), and the collection of hot
    Jupiters analyzed in Appendix A.
    {\bf \it Top:}
    The key parameters relevant to eccentricity damping.  Solid
    squares represent planets with a securely detected nonzero
    eccentricity. Lines of constant damping timescale are drawn based
    on Equation~\ref{eq:de_dt} and assuming $Q_{\rm p}' = 10^5$.
    WASP-4b has one of the shortest eccentricity damping timescales.
    {\bf \it Middle:} 
    Plotted are the key parameters relevant to orbital decay.  Lines
    of constant decay timescale are drawn based on
    Equation~\ref{eq:da_dt}), assuming $Q_\star' = 10^7$.  WASP-4b has
    a relatively short orbital decay timescale, although it is not as
    extreme a case in this regard as it is for eccentricity damping.
    {\bf \it Bottom:}
    A Hertzsprung-Russell diagram for hot Jupiter hosts. WASP-4
    appears to be on the main sequence.
    \label{fig:context}
  }
\end{figure}

>>>>

\begin{abstract}
    The Transiting Exoplanet Survey Satellite (TESS) recently observed
    18 transits of the hot Jupiter WASP-4b.  The sequence of transits
    occurred $81.5 \pm 11.7$~seconds earlier than had been predicted,
    based on data stretching back to 2007.  This is unlikely
    to be the result of a clock error, because TESS observations of
    other hot Jupiters (WASP-6b, 18b, and 46b) are compatible with a
    constant period, ruling out an 81.5-second offset at the
    6.4$\sigma$ level.  The 1.3-day orbital period of WASP-4b appears
    to be decreasing at a rate of $\dot{P} = -12.6 \pm 1.2$
    milliseconds per year.  This might be caused by tidal orbital
    decay or apsidal precession, although both interpretations have
    shortcomings.  The gravitational influence of a third body is another
    possibility, although at present there is no evidence for such a
    body. Further observations are needed to confirm and
    understand the timing variation.
\end{abstract}

@@

Second, long-term timing studies may reveal apsidal precession, {\it
  i.e.}, the rotation of the orbital ellipse within the orbital
plane. Apsidal precession has long been observed in eclipsing binaries
\citep[{\it e.g.},][]{
  schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015}.
For exoplanets, precessing orbits have been detected in a handful of
cases, including circumbinary systems (Kepler-413
\citealt{kostov_kepler-413b_2014}; Kepler-453
\citealt{welsh_kepler_2015}, planets orbiting rapidly rotating stars
(Kepler-13
\citealt{szabo_spin-orbit_2012,szabo_mapping_2014},~\citealt{masuda_spin-orbit_2015};
and systems with multiple interacting giant planets (Kepler-108
\citealt{mills_kepler-108_2017}; Kepler-693
\citealt{masuda_eccentric_2017}).  Apsidal precession is not regularly
observed in hot Jupiter systems because their orbits are nearly
circular, which may itself be a consequence of star-planet tides.  If
it could be observed, then \citet{ragozzine_probing_2009} showed that
it would be possible to measure the planet's Love number, which would
be a valuable constraint on the planet's interior.

@@

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=0.49\textwidth]{f2.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Phase-folded lightcurve of WASP-4b.} Black points are
        TESS data. Yellow points are binned measurements.  The bottom
        panel shows the residuals.  The fit to the phase-folded
        transit (blue line) is used when measuring mid-transit times for
        the individual transits (see text).
        \label{fig:phasefold}
    }
\end{figure}

@@

We began our analysis with the Presearch Data Conditioning (PDC)
lightcurve \citep{smith_kepler_apertures_2017,smith_kepler_PDC_2017}.
We processed the lightcurve as follows.  First, we removed all points
with non-zero quality flags.  This removed data contaminated by coarse
spacecraft pointing, cosmic rays, and other annoyances
\citep{tess_data_product_description_2018}.  We also removed the data
within the first and last hours of both orbits, because of ramp-like
systematic effects that appear during those time ranges. We also
removed the data that might have been adversely affected by ``momentum
dumps,'' the firing of thrusters and resetting of reaction wheels\footnote{\url{archive.stsci.edu/hlsps/tess-data-alerts/hlsp_tess-data-alerts_tess_phot_s01_tess_v1_release-notes.pdf}}
that took place every 2.5 days during sector 2.
The data during these events were assigned quality flags corresponding
to ``Reaction Wheel Desaturation Event'' and ``Manual Exclude''.  For
WASP-4, these flags were simultaneously set for 54 distinct cadences,
and there were 10 momentum dumps, averaging about 10 minutes of
flagged data per dump.  Out of caution, we clipped out an additional
10 minutes before and after every momentum dump.

@@

Using the cleaned PDC lightcurve, we used the Box Least Squares
algorithm \citep{kovacs_box-fitting_2002} to estimate the orbital
period, transit duration, and a reference epoch using the TESS data
alone.  Based on the results, we isolated the data within 4 transit
durations of each transit midpoint.  To find the transit parameters
that best fit the data, we first fitted a line to the out-of-transit
flux measurements surrounding each transit, and divided it out.  We
then created a phase-folded lightcurve and fitted a standard transit
model using the analytic formulae given by
\citet{mandel_analytic_2002} and implemented by
\citet{kreidberg_batman_2015}.  We assumed the orbit to be circular.
The free parameters were the reference epoch, the planet to star
radius ratio $R_{\rm p}/R_\star$, the orbital distance to stellar
radius ratio $a/R_\star$, the inclination $i$, two quadratic
limb-darkening coefficients $(u_{\rm linear}, u_{\rm quad})$, and the
orbital period $P$.

@@

To measure the transit times, we returned to the `cleaned' PDC time
series and fitted the data surrounding each transit separately, with
four free parameters: the time of mid-transit $t_{\rm tra}$, the
planet-to-star radius ratio, and the slope and intercept of a linear
trend to account for any slow variations unrelated to the transit.  We
fixed the remaining parameters at the values that had been determined
from the phase-folded TESS lightcurve.  The uncertainty in each data
point was set equal to the root-mean-square (rms) level of the
out-of-transit data.

To verify that the measured uncertainties are plausible, we computed
the reduced $\chi^2$ for a linear ephemeris fit to the measured TESS
transit times.  We found that $\chi^2 = 9.2$, with $n=16$ degrees of
freedom.  The variance of the $\chi^2$ distribution is $2n$, so we
would expect $\chi^2 = 16 \pm 5.7$.  Visually inspecting the residuals
showed that the error variance had been overestimated, so we
multiplied the measured TESS errors by a factor $f=0.76$, forcing a
reduced $\chi^2$ of unity.  This lowered the mean uncertainty of the
transit midtimes from $29.8$ to $22.6$ seconds.  We verified that
omitting this step did not appreciably alter any of our conclusions.

@@

\startdata
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.15201$              & $+0.00040$, $-0.00033$      & A \\
  $i$~[deg]                                  & $89.06$                & $+0.65$, $-0.84$            & A \\
  $a/R_\star$                                & $5.451$                & $+0.023$, $-0.052$          & A \\
  $u_{\rm linear}$                           & $0.382$                & ---                         & A \\
  $u_{\rm quad}$                             & $0.210$                & ---                         & A \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & B \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & C \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & C \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & C \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & D \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & F \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & E \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.711$                & $+0.022$, $-0.048$          & E \\
  $M_\star$~[M$_{\odot}$]                    & $0.864$                & $+0.084$, $-0.090$          & E \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & G \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0226$               & $+0.0007$, $-0.0008$        & E \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.186$                & $+0.090$, $-0.098$          & E \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.321$                & $\pm 0.039$                 & E \\
\enddata

@@

We calculated the stellar and planetary parameters in the following
way.  We computed the star's spectral energy distribution based on the
{\it Gaia} DR2 parallax (after making the small correction advocated
by \citealt{stassun_evidence_2018}) and the broadband magnitudes from
the available all-sky catalogs: $G$ from {\it Gaia\/} DR2, $B_T$
and $V_T$ from {\it Tycho-2}, $BVgri$ from {\it APASS}, $JHK_S$ from
{\it 2MASS}, and the {\it WISE}~1--4 passbands, thus spanning the
wavelength range 0.4--22~$\mu$m.  We adopted the effective temperature
from the work by \citet{doyle_accurate_2013}, who determined the
spectroscopic parameters of WASP-4 using high-signal-to-noise
observations with the High Accuracy Radial-velocity Planet Searcher
(HARPS).  Then, we determined the stellar radius through the
combination of the bolometric luminosity and the effective
temperature, using the Stefan-Boltzmann law.  To determine the stellar
mass, we first computed the mean stellar density based on the value of
$a/R_\star$ that gave the best fit to the phase-folded TESS lightcurve
(for the relevant equation, see \citealt{seager_unique_2003} or
\citealt{winn_exoplanet_2010}).  The mass was calculated from the
radius and density, and the orbital distance was also calculated from
the radius and $a/R_\star$.  The planetary radius was calculated as
the product of $R_\star$ and $R_{\rm p}/R_\star$.  Finally, the planet
mass was calculated based on the stellar mass, the radial-velocity
amplitude observed by \citet{triaud_spin-orbit_2010}, and the orbital
inclination.

@@

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{ {\bf TESS saw WASP-4b transit earlier than expected.}
      Both plots show the deviations between the observed and
      calculated transit times, where the calculation is based only on
      the pre-TESS data and assumes a constant period.  The blue bands
      depict the $\pm$$1\sigma$ credible interval of the predicted
      times.  {\it Top:} The full timing dataset spans 11 years. The
      darkest points correspond to the most precise data.  {\it
        Bottom:} Close-up of the TESS observations. The red band shows
      the average deviation of the TESS transits, which arrived $81.5 \pm
      11.7\ {\rm seconds}$ earlier than predicted.
        \label{fig:arrived_early}
    }
\end{figure}

@@

We also compiled all the available occultation times, which are given
in Table~3.  The tabulated values have been corrected for the
light-travel time across the diameter of the orbit by subtracting
$2a/c = 22.8$ seconds from the observed time.
\citet{beerer_secondary_2011} observed two occultations of WASP-4b
using warm Spitzer in the 3.6\,$\mu$m and 4.5\,$\mu$m bands.
\citet{caceres_ground-based_2011} detected an occultation from the
ground in the $K_S$ band, and gave a time in HJD, without specifying
the time standard.  We assumed the standard was UTC, and performed the
appropriate corrections to convert to BJD$_{\rm TDB}$.  We
also verified that none of our conclusions would be changed if this
assumption was mistaken. Finally, \citet{zhou_secondary_2015} observed an
occultation with the Anglo-Australian Telescope.  They did not
report the observed midpoint, but they did report a result for
$e\cos\omega$ based upon the observed midpoint.  We calculated the
implied midpoint using the formula \citep[{\it
e.g.},][]{winn_exoplanet_2010}
\begin{equation}
  t_{\rm occ}(E) =
  t_0 +  P E  +
  \frac{P}{2} \left( 1 + \frac{4}{\pi} e\cos\omega \right).
  \label{eq:occultation_time}
\end{equation}
In total, there are four occultation times.

@@

In the decreasing-period model, the period derivative is
\begin{equation}
\dot{P}
  = - (3.98 \pm 0.38)\times 10^{-10}
  = - 12.6 \pm 1.2~{\rm ms}\,{\rm yr}^{-1}.
  \label{eq:dP_dt_obs}
\end{equation}
For comparison, the best-fitting period derivative of WASP-12b is
$\dot{P} = -29 \pm 3\,{\rm ms}\,{\rm yr}^{-1}$
\citep{maciejewski_departure_2016,patra_2017}.  If both planets are
truly falling onto their stars, then WASP-4b is falling at about half
the rate of WASP-12b.  In the precession model, the best-fit
eccentricity is
\begin{equation}
  e = (1.83^{+ 1.88}_{- 0.75})\times10^{-3}
\end{equation}
The longitude of periastron advances by $\dot{\omega} =
14.0^{+4.9}_{-3.5}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period is $26^{+9}_{-7}$ years.  All of the best-fitting parameters
(the medians of the posterior distributions) and the 68\% credible
intervals are reported in Table~4.

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.385\textwidth]{f5.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf WASP-4b in the context of other hot Jupiters.}
    Most of the data in these plots are from \citet{bonomo_gaps_2017},
    who measured the eccentricities using radial velocities.  The
    colored symbols highlight WASP-4, WASP-12 (which also shows
    evidence for a decreasing period), and the collection of hot
    Jupiters analyzed in Appendix A.
    {\bf \it Top:}
    The key parameters relevant to eccentricity damping.  Solid
    squares represent planets with a securely detected nonzero
    eccentricity. Lines of constant damping timescale are drawn based
    on Equation~\ref{eq:de_dt} and assuming $Q_{\rm p}' = 10^5$.
    WASP-4b has one of the shortest eccentricity damping timescales.
    {\bf \it Middle:} 
    Plotted are the key parameters relevant to orbital decay.  Lines
    of constant decay timescale are drawn based on
    Equation~\ref{eq:da_dt}, assuming $Q_\star' = 10^7$.  WASP-4b has
    a relatively short orbital decay timescale, although it is not as
    extreme a case in this regard as it is for eccentricity damping.
    {\bf \it Bottom:}
    A Hertzsprung-Russell diagram for hot Jupiter hosts. WASP-4
    appears to be on the main sequence.
    \label{fig:context}
  }
\end{figure}
